### 2016-11-16 paper/intro.tex
minor change in intro

Although regression testing is a recognized problem both in industry
and academia, to the best of our knowledge no prior work has
investigated the regression testing problem in open-source projects.
The alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
server farm (for increased security) to automate the testing process
may be a legitimate approach to mitigate the regression testing
problem at large organizations.  However, building such infrastructure
may not be feasibile for open-source and low-budget projects.  For
example, as of August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  This paper assumes that, given that it
is not rare for open-source projects to face high testing costs, it is
important to run test suites efficiently using commodity hardware.

>>>>

Although regression testing is a recognized problem both in industry
and academia, to the best of our knowledge no prior work has
investigated the regression testing problem in open-source projects.
The alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
server farm (for increased security) may be a legitimate approach to
mitigate the regression testing problem at large organizations.  For
example, as of August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  Given that it is not rare for
open-source projects to face high testing costs, this paper assumes
that it is not economically viable for these projects to build
high-end testing infrastructure.  Consequently, it is important to run
test suites efficiently using commodity hardware in these scenarios.
